Titeln på avhandlingens språk

### 2023-03-09 body/part1/chapter2-relatedwork/relatedwork.tex
relwork

>>>>

\textcite{choi2022emulating}: XREmul, input emulation tool for XR.
Similar to \cite{munro2016aaremu}, traces of inputs are pre-recorded and then replayed.
Allows for abstraction of inputs in general classes for device-agnostic inputs.
Paper highlights the challenges of deterministic trace (leaves solution to future work).
